---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# saeHB.zinb

<!-- badges: start -->
<!-- badges: end -->

Provides function for area level of small area estimation using hierarchical Bayesian (HB) method with Zero-Inflated Binomial distribution for variables of interest. Some dataset produced by a data generation are also provided. The 'rjags' package is employed to obtain parameter estimates. Model-based estimators involves the HB estimators which include the mean, the variation of mean, and the quantile.

## Author
Rizqina Rahmati , Azka Ubaidillah

## Maintaner
Rizqina Rahmati <221810583@stis.ac.id>

## Installation

You can install the development version of saeHB.ZIB from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rizqinaR/saeHB.ZIB")
```

## Function

* `ziBinomial()` This function gives small area estimator under Zero Inflated Binomial Model and is implemented to variable of interest (y) that assumed to be a Zero Inflated Binomial Distribution. The range of data is (y >= 0)

## Example

This is a basic example of using `ziBinomial()` function to make an estimate based on synthetic data in this package

```{r example}
library(saeHB.ZIB)
## For data without any non-sampled area
data(dataZIB)       # Load dataset
## For data with non-sampled area use dataHNBNs
## Fitting model
result <- ziBinomial(y ~ x1 + x2, n.samp = "s", data=dataZIB)
```

Small Area mean Estimates

```r
result$Est
```

Estimated model coefficient

```r
result$coefficient
```

Estimated random effect variances

```r
result$refVar
```

## References
*W. Bodromurti, “ZERO INFLATED BINOMIAL MODELS IN SMALL AREA ESTIMATION WITH APPLICATION TO INFANT MORTALITY DATA IN INDONESIA”, in Thesis IPB University Scientific Repository, 2017.
*Matranga, D, Firenze, A, Vullo, A. Can bayesian models play a role in dental caries epidemiology? Evidence from an application to the BELCAP data set. Community Dent Oral Epidemiol 2013; 41: 473– 480. © 2013 John Wiley & Sons A/S. Published by John Wiley & Sons Ltd.
*B. Hartono, “Kajian Pendugaan Area Kecil dengan Model Zero Inflated Binomial (Studi Kasus Pengangguran di Provinsi Jambi)”, in Thesis IPB University Scientific Repository, 2018.
*Hall DB. Zero-inflated Poisson and binomial regression with random effects: a case study. Biometrics 2000;56(4):1030–9.



